---
title: "Homework 5"
author: "Yining Chen"
date: "2022-11-13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(broom)
```

## Problem 2
```{r}

a = rnorm(10, mean = 0, sd = 1)

tidy(t.test(a,mu=0))[3]
```


## Problem 3
```{r}
set.seed(1)

sim_mean = function(n, mu = 0, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      p_value = broom::tidy(t.test(x, mu = 0))[3]
    )
}

output = vector("list", 5000)

for (i in 1:5000) {
  output[[i]] = sim_mean(30)

}

sim_results = bind_rows(output)
```

```{r}
set.seed(1)
sim_results_df = 
  expand_grid(
    true_mu = c(0:6),
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(.x = true_mu, ~ sim_mean(30,mu = .x))
  ) %>% 
  unnest(estimate_df)
```

```{r}
sim_results_df <- sim_results_df %>% 
  mutate(p.value=p_value$p.value)%>%select(1,3,5)
```

```{r}
for (i in 0:6) {
  proportions[i+1] = nrow( filter(sim_results_df, true_mu==i&p.value<0.05))/5000
}

power <- df <- data.frame (mu  = str_c("u = ", c(0:6)),
                  proportion=proportions
                  )
                  
```

```{r}
ggplot(data=power, aes(x=mu, y=proportion)) +
  geom_bar(stat="identity",fill="steelblue")+
  theme_minimal()+
  xlab(expression(paste("True ", mu)))+
  ylab("Power")+
  ggtitle(expression(paste("Bar Plot of Power and True Values of ", mu)))+
  geom_text(aes(label=proportion), vjust=1.2, color="white",
            position = position_dodge(0.9), size=3)
```
From the above bar plot, we can tell that the proportion of times the null was rejected increases as the true value of μ gets larger. When μ is equal to 4,the proportion approximately reaches to 1. There is a positive asscociation between effect size and power. Therefore, to increase the power of our study, we could use potent interventions that have bigger effects.
.
```{r}
est_mu <- sim_results_df %>% 
  pivot_longer(
    mu_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter, true_mu) %>% 
  summarize(
    emp_mean = mean(estimate))
```

```{r}
est_mu_rej <- sim_results_df %>% 
  filter(p.value<0.05)%>%
  pivot_longer(
    mu_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter, true_mu) %>% 
  summarize(
    emp_mean_rej = mean(estimate))

total <- merge(est_mu,est_mu_rej,by=c("true_mu"))%>%select(1,3,5)

ggplot(total,aes(x=true_mu, y=emp_mean)) +
  geom_line(aes(color="All samples"))+
  geom_line(aes(y = emp_mean_rej,color="Null was rejected"),linetype="dashed",size=1)+
  xlab(expression(paste("True ", mu)))+
  ylab(expression(paste("Average Estimate of ", mu)))+
    geom_point(color = "red")+
  ggtitle(expression(paste("Plot of Estimated and True Values of ", mu)))
```
The sample average of μ̂ across tests for which the null is rejected is not approximately equal to the true value of μ when μ is small. This is because when the value of μ is close to the hypothesized value of zero, there is only a small proportion of tests for which the null is rejected. Among those tests,  μ̂ is not likely to be close to the true value.

