---
title: "Homework 5"
author: "Yining Chen"
date: "2022-11-13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(broom)
library(purrr)
```

## Problem 2

This data records homicides in 50 large U.S. cities which contains 52179 observations and 12 variables. The variables including case id, reported date of murder, victim’s last name, victim’s first name, victim’s race, victim’s age, victim’s sex, city, state, latitidue, longitude, and disposition of the case.

```{r,warning=FALSE,message=FALSE}
homicide <- read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")

homicide <- homicide%>%
  mutate(city_state=str_c(city, ",",state))%>%
  relocate(city_state)
  

homicide %>%
  group_by(city) %>%
  summarise(
    unsolved = sum(disposition=="Closed without arrest"| disposition =="Open/No arrest"),
    n = n()) %>%
  knitr::kable(col.names = c("City", "Unsolved Homicides", "Total Homicides"))


```

```{r}
prop.test(x=1825, n=2827) %>% broom::tidy()
```

```{r}
prop_test <- function(df) {
  
  city_sum <- df %>%
  summarise(
    unsolved = sum(disposition=="Closed without arrest"| disposition =="Open/No arrest"),
    n = n()
  )

  test <- prop.test(
    x = city_sum %>% pull(unsolved),
    n = city_sum %>% pull(n))
  return(test)
}

```

```{r,warning=FALSE}
results = 
  homicide %>%
  nest(data = uid:disposition) %>%
  mutate(
    tests = map(data, prop_test),
    tidy_tests = map(tests, broom::tidy)
    ) %>% 
    select(city_state, tidy_tests) %>% 
    unnest(tidy_tests) %>% 
    select(city_state, estimate, starts_with("conf"))

head(results) %>% 
  knitr::kable()

```
```{r}
results%>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point(color="red",size=1) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +  
  theme(axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust = 1))+
  xlab("City")+
  ylab("Proportion")+
  ggtitle("Proportion of unsolved homicides and the CIs for each city")
```


## Problem 3
```{r}
set.seed(1)

sim_mean = function(n, mu = 0, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      p_value = broom::tidy(t.test(x, mu = 0))[3]
    )
}

output = vector("list", 5000)

for (i in 1:5000) {
  output[[i]] = sim_mean(30)

}

sim_results = bind_rows(output)
```

```{r}
set.seed(1)
sim_results_df = 
  expand_grid(
    true_mu = c(0:6),
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(.x = true_mu, ~ sim_mean(30,mu = .x))
  ) %>% 
  unnest(estimate_df)
```

```{r}
sim_results_df <- sim_results_df %>% 
  mutate(p.value=p_value$p.value)%>%select(1,3,5)
```

```{r}

proportions = sim_results_df%>% filter(p.value<0.05)%>%group_by(true_mu)%>%summarise(n=n())

power <- data.frame (mu  = str_c("u = ", c(0:6)),
                  proportion=proportions$n/5000
                  )
                  
```

```{r}
ggplot(data=power, aes(x=mu, y=proportion)) +
  geom_bar(stat="identity",fill="steelblue")+
  theme_minimal()+
  xlab(expression(paste("True ", mu)))+
  ylab("Power")+
  ggtitle(expression(paste("Bar Plot of Power and True Values of ", mu)))+
  geom_text(aes(label=proportion), vjust=1.2, color="white",
            position = position_dodge(0.9), size=3)
```
From the above bar plot, we can tell that the proportion of times the null was rejected increases as the true value of μ gets larger. When μ is equal to 4,the proportion approximately reaches to 1. There is a positive asscociation between effect size and power. Therefore, to increase the power of our study, we could use potent interventions that have bigger effects.
.
```{r}
est_mu <- sim_results_df %>% 
  pivot_longer(
    mu_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter, true_mu) %>% 
  summarize(
    emp_mean = mean(estimate))
```

```{r}
est_mu_rej <- sim_results_df %>% 
  filter(p.value<0.05)%>%
  pivot_longer(
    mu_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter, true_mu) %>% 
  summarize(
    emp_mean_rej = mean(estimate))

total <- merge(est_mu,est_mu_rej,by=c("true_mu"))%>%select(1,3,5)

ggplot(total,aes(x=true_mu, y=emp_mean)) +
  geom_line(aes(color="All samples"))+
  geom_line(aes(y = emp_mean_rej,color="Null was rejected"),linetype="dashed",size=1)+
  xlab(expression(paste("True ", mu)))+
  ylab(expression(paste("Average Estimate of ", mu)))+
    geom_point(color = "red")+
  ggtitle(expression(paste("Plot of Estimated and True Values of ", mu)))
```

The sample average of μ̂ across tests for which the null is rejected is not approximately equal to the true value of μ when μ is small. This is because when the value of μ is close to the hypothesized value of zero, there is only a small proportion of tests for which the null is rejected. Among those tests,  μ̂ is not likely to be close to the true value.

